---
title: "Plots From Function Word Data From Childes"
author: "Sunny Zhou"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
require(stats)
library(childesr)
library(tidyverse)
library(feather)
library(data.table)
library(dplyr)
library(radiant)
library(zipfR)
library(utilities)
```


#Load the data from local files
```{r}
#read the raw data
# exclusions <- read.csv(file = '../raw_data/token_exclusions.csv')
english_tokens<- read_feather(path = '../raw_data/english_tokens.feather')
# speaker_stats<- read.csv(file="../raw_data/speaker_function_word_stats.csv")
# all_english_tokens <- read_feather(path = '../raw_data/all_english_function_word_tokens.feather')
processed_tokens<-read_feather(path='../processed_data/english_tokens_processed.feather')
```

#Adding column to processed_tokens with the frequencies of words based on speaker role.
```{r general data}
# PDF <- dzipf(x=1:n_distinct(processed_tokens_counts$gloss), N=length(processed_tokens_counts$gloss), s=2)

#plot the population ages
processed_tokens%>%filter(speaker=="child")%>%group_by(age)%>%distinct(speaker_id)%>%pull(age)%>%table()%>%plot(main="Children Population Ages",
  xlab="Age (months)", ylab="Frequency")

# counting occurrence of tokens based on speakers
processed_tokens<-processed_tokens%>%group_by(speaker)%>%mutate(num_speakers=n())
processed_tokens<-processed_tokens%>%group_by(speaker,gloss)%>%mutate(n_general=n())
processed_tokens<-processed_tokens%>%mutate(rf_general=round(n_general/num_speakers,digits=5))
processed_tokens<-processed_tokens%>%mutate(logf_general=round(log(n_general),digits=5))

# counting occurrence of tokens based on speakers in age
processed_tokens<-processed_tokens%>%group_by(speaker,age)%>%mutate(num_speakers_by_abin=n())
processed_tokens<-processed_tokens%>%group_by(speaker,age,gloss)%>%mutate(n_abin=n())
processed_tokens<-processed_tokens%>%mutate(rf_abin=round(n_abin/num_speakers_by_abin,digits=5))
processed_tokens<-processed_tokens%>%mutate(logf_abin=round(log(n_abin),digits=5))

# counting occurrence of tokens based on speakers in age and function word category
processed_tokens<-processed_tokens%>%group_by(speaker,age,functionword_category)%>%mutate(n_cat=n())
processed_tokens<-processed_tokens%>%mutate(rf_cat=round(n_cat/num_speakers_by_abin,digits=5))
processed_tokens<-processed_tokens%>%mutate(logf_cat=round(log(n_cat),digits=5))

## removing duplicate words
processed_tokens_counts<-processed_tokens%>%distinct(gloss,speaker,age,.keep_all= TRUE)

```

```{r cleaning data}
# processed_tokens_counts$gloss<-processed_tokens_counts$gloss%>%factor(levels=processed_tokens_counts)
parent_data<-processed_tokens_counts%>%filter(speaker=="parent")%>%distinct(gloss,speaker_id,.keep_all= TRUE)
child_data<-processed_tokens_counts%>%filter(speaker=="child")%>%distinct(gloss,speaker_id,.keep_all= TRUE)
```


#Plotting general plots for children and parents

```{r general plots}
#raw frequency plot
child_data[0:100,]%>%ggplot(aes(x=rank(reorder(gloss,-n_general)), y=n_general,color=functionword_category)) +
  geom_point()+
  theme_minimal()+labs(title="Children Token Raw Frequencies", 
         x="Frequency Rank", y = " Raw Frequency")+scale_x_continuous(breaks = seq(0, 100, by = 10))+ labs(color='Lexical Category') 
# ggsave("child_general.png")


#relative frequency plot
child_data[0:100,]%>%ggplot(aes(x=rank(reorder(gloss,-rf_general)), y=rf_general,color=functionword_category)) +
  geom_point()+
  theme_minimal()+labs(title="Children Token Relative Frequencies", 
         x="Frequency Rank", y = " Relative Frequency")+scale_x_continuous(breaks = seq(0, 100, by = 10))+ labs(color='Lexical Category') 
# ggsave("child_general_rf.png")

child_data[0:100,]%>%ggplot(aes(x=rank(reorder(gloss,-logf_general)), y=logf_general,color=functionword_category)) +
  geom_point()+
  theme_minimal()+labs(title="Children Token Log Frequencies", 
         x="Frequency Rank", y = " Log Frequency")+scale_x_continuous(breaks = seq(0, 100, by = 10))+ labs(color='Lexical Category') 
# ggsave("child_general_logf.png")

#raw frequency plot
parent_data[0:100,]%>%ggplot(aes(x=rank(reorder(gloss,-n_general)), y=n_general,color=functionword_category)) +
  geom_point()+
  theme_minimal()+labs(title="Parent Token Raw Frequencies", 
         x="Frequency Rank", y = " Raw Frequency")+scale_x_continuous(breaks = seq(0, 100, by = 10))
# ggsave("parents_general.png")


#relative frequency plot
parent_data[0:100,]%>%ggplot(aes(x=rank(reorder(gloss,-rf_general)), y=rf_general,color=functionword_category)) +
  geom_point()+
  theme_minimal()+labs(title="Parent Token Relative Frequencies", 
         x="Frequency Rank", y = " Relative Frequency")+scale_x_continuous(breaks = seq(0, 100, by = 10))
# ggsave("parents_general_rf.png")

parent_data[0:100,]%>%ggplot(aes(x=rank(reorder(gloss,-logf_general)), y=logf_general,color=functionword_category)) +
  geom_point()+
  theme_minimal()+labs(title="Parent Token Log Frequencies", 
         x="Frequency Rank", y = " Log Frequency")+scale_x_continuous(breaks = seq(0, 100, by = 10))
# ggsave("parents_general_log.png")
```

```{r}
ordered_words<-levels(reorder(processed_tokens$gloss,-processed_tokens$n_general))
for (x in ordered_words[1:20]){
token_data<-processed_tokens%>%filter(gloss==x)%>%distinct(gloss,speaker,age,.keep_all= TRUE)
# #raw frequency plot
# print(token_data%>%ggplot(aes(x=age, y=n_abin,color=speaker)) +
#   geom_point()+
#   theme_minimal()+labs(title=sprintf("%s Token Raw Frequencies",x), 
#          x="Age Bins (months)", y = " Raw Frequency"))

#relative frequency plot
print(token_data%>%ggplot(aes(x=age, y=rf_abin,color=speaker)) +
  geom_point()+
  theme_minimal()+labs(title=sprintf("\"%s\" Token Relative Frequencies",x),
         x="Age Bins (months)", y = " Relative Frequency")+scale_x_continuous(breaks = seq(0, 72, by = 12)))
ggsave(sprintf("%s.png",x))

# 
# token_data%>%ggplot(aes(x=age, y=logf_abin,color=speaker)) +
#   geom_point()+
#   theme_minimal()+labs(title=sprintf("%s Token Log Frequencies",x), 
#          x="Age Bins (months)", y = " Log Frequency")
# Sys.sleep(2)
}
```

```{r}
ordered_category<-levels(reorder(processed_tokens$functionword_category,-processed_tokens$n_cat))
for (x in ordered_category){
cat_data<-processed_tokens%>%filter(functionword_category==x)%>%distinct(functionword_category,speaker,age,.keep_all= TRUE)
# #raw frequency plot
# print(token_data%>%ggplot(aes(x=age, y=n_abin,color=speaker)) +
#   geom_point()+
#   theme_minimal()+labs(title=sprintf("%s Token Raw Frequencies",x), 
#          x="Age Bins (months)", y = " Raw Frequency"))

#relative frequency plot
print(cat_data%>%ggplot(aes(x=age, y=rf_cat,color=speaker)) +
  geom_point()+
  theme_minimal()+labs(title=sprintf("\"%s\" Word Relative Frequencies",x),
         x="Age Bins (months)", y = " Relative Frequency")+scale_x_continuous(breaks = seq(0, 72, by = 12)))
ggsave(sprintf("%s.png",x))

# 
# token_data%>%ggplot(aes(x=age, y=logf_abin,color=speaker)) +
#   geom_point()+
#   theme_minimal()+labs(title=sprintf("%s Token Log Frequencies",x), 
#          x="Age Bins (months)", y = " Log Frequency")
# Sys.sleep(2)
}
```
* Logical Connectives: no, not, n't, and, or, if, nor
* Quantifiers: none, some, each, every, all, most, few, many, several, a few, both, everyone, someone, somebody, everybody, nonone, everything, something, nowhere, somewhere, everywhere
* Comparative Quantity: more, less, much
* Numerals: 1. numbers: one, two, three, four, five, six, seven, eight, nine, ten 2. ordinals: first, second, third, fourth fifth, last
* Modals: can, could, need, may, might, should, ought, must, maybe, perhaps, shall
* Negative Polarity Items: any, anyone, anything, anyhow, anywhere, anything, anyway, ever, yet
* Definiteness and Demonstratives: 1. Definite: the, a, an 2. Demonstratives: this, that, these, those
* Temporals: 1. Quantifiers: always, usually, seldom, never, sometimes, now, often, once 2. Connectives: when, while, after, before, then, until, since, whenever, during
* Interrogatives: who, when, what, whose, where, how, why, whom
* Locatives: on, in, out, up, down, under, above, below, along, over, behind, across, beside, between, beyond, inside, outside, into, near, onto, toward
* Causal Connectives: because, therefore
* Contrast Connectives: but, although
* Additives: again, too, also, another, other, others, still
* Focus Particles: even, only, indeed
* Other: either, neither, whether as, else, almost, already, except, for, from, instead, same, different, such, with, without, about, by, very



